Coupling finite and boundary element methods to solve the Poisson--Boltzmann equation for electrostatics in molecular solvation

### 2023-05-05 main.tex
remove my comments, I'll make them on GitHub instead
Changes discussed on 5/05

\newcommand{\mscomment}[1]{\textbf{\color{red}[Matthew: #1]}}

@@

% makes references listed with 1., 2., etc.  
0  \makeatletter
  \renewcommand\@biblabel[1]{#1.}
  \makeatother

@@

\subsection*{\sffamily \large ACKNOWLEDGMENTS}
MB acknowledges the support from Kingston University through First Kingston University Grant. \\
CDC acknowledges the support from CCTVal through ANID PIA/APOYO AFB220004.
%((Place Acknowledgments here))

\subsection*{\sffamily \large DATA AVAILABILITY STATEMENT}
All codes to reproduce the results of this manuscript can be found in the Github repository \url{https://github.com/MichalBosy/FEM_BEM_coupling/}

>>>>

@@

% makes references listed with 1., 2., etc.  
\makeatletter
  \renewcommand\@biblabel[1]{#1.}
  \makeatother

@@

\subsection*{\sffamily \large ACKNOWLEDGMENTS}
MB acknowledges the support from Kingston University through First Kingston University Grant. \\
CDC acknowledges the support from CCTVal through ANID PIA/APOYO AFB220004.\\
MS needs to look up the grant he has to put here. \\
EB acknowledges support from EPSRC grants EP/V050400/1 and EP/W007460/1 \\
We would like to thank J{\o}rgen Dokken for his help with various implementation details related to FEniCSx.
%((Place Acknowledgments here))

\subsection*{\sffamily \large DATA AVAILABILITY STATEMENT}
All codes to reproduce the results of this manuscript can be found in the GitHub repository \url{https://github.com/MichalBosy/FEM_BEM_coupling/}, alongside links to Docker images
that include the codes alongside installations of appropriate versions of Bempp-cl and FEniCSx.

### 2023-05-05 methods.tex
remove my comments, I'll make them on GitHub instead
Changes discussed on 5/05

Several possible boundary integral formulations of \eqref{eq:pbe} exist.~\cite{search2022towards} The simplest form was presented by Yoon and Lenhoff in 1991\cite{YoonLenhoff1990} and is known as the \emph{direct formulation}. However, the resulting system is usually ill-conditioned. Here, we use the better-conditioned formulation presented by Lu and co-workers,~\cite{LuETal2006,LuETal2009,debuhr2016dashmm} which reads
%
\begin{align}\label{eq:lu}
    \tfrac{\phi_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) - \left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)\phi_2 + \left(V_Y^\Gamma - V_L^\Gamma\right)\lambda_2 &= \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|},
     \nonumber \\
    \tfrac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)\phi_2 +  \tfrac{\lambda_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) + \left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\lambda_2 &= \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}\right),
\end{align}
where $\phi_2 = \phi_2(\mathbf{x}_\Gamma)$ is the potential on $\Gamma$ as we approach from $\Omega_2$ ({\it ie.} the exterior Dirichlet trace),
and $\lambda_2 = \frac{\partial}{\partial \mathbf{n}}\phi_2$ is the normal derivative $\Gamma$ as we approach from $\Omega_2$ ({\it ie.} the exterior Neumann trace).
Note that we could use equations \eqref{eq:pbe3} and \eqref{eq:pbe4} to rewrite Equation \eqref{eq:lu} in terms of the interior traces $\phi_1$ and $\lambda_1$.
The operators $V$, $K$, $K^{\prime}$, and $W$ that appear in Equation \eqref{eq:lu} are the single-layer, double-layer, adjoint double-layer, and hypersingular operators for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels. These are defined %in Equation~\eqref{eq:single_double} and 
by
%
\begin{align}\label{eq:all_op}
V_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma g_i(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
K_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma \frac{\partial g_i}{\partial\mathbf{n}'}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
K^{\prime\Gamma}_i\varphi (\mathbf{x}) &= \oint_\Gamma \frac{g_i}{\partial\mathbf{n}}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
W^\Gamma_i\varphi (\mathbf{x}) &= - \oint_\Gamma \frac{\partial^2 g_i}{\partial\mathbf{n}'\partial\mathbf{n}}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',
\end{align}
%
where $i \in \{L,Y\}$, $\varphi(\mathbf{x})$ can be any distribution over $\Gamma$, and %Green's functions $g_L, g_Y$ were defined in Equation~\eqref{eq:green_func}.
\begin{align}\label{eq:green_func}
g_L(\mathbf{x},\mathbf{x}')=\frac{1}{4\pi|\mathbf{x}-\mathbf{x}'|} \nonumber \\
g_Y(\mathbf{x},\mathbf{x}')=\frac{e^{-\kappa|\mathbf{x}-\mathbf{x}'|}}{4\pi|\mathbf{x}-\mathbf{x}'|}
\end{align}
are the corresponding free-space Green's functions.

@@

Having computed the electrostatic potential with Eq.~\eqref{eq:lu}, we obtain the reaction potential ($\phi_r$) in Eq.~\eqref{eq:dG} by subtracting the Coulombic component from $\phi_1$. This gives\cite{CooperBardhanBarba2014}
%
\begin{align} \label{eq:phi_reac}
\phi_{r}(\mathbf{r}) = - K_{L}^{\Gamma} \phi_1(\mathbf{r}) + V_{L}^{\Gamma}  \lambda_1(\mathbf{r}),
\end{align}
%
where $\mathbf{r}\in\Omega_1$, and we can obtain $\phi_2$ and $\lambda_2$ from $\phi_1$ and $\lambda_1$ by applying the interface conditions \eqref{eq:pbe3} and \eqref{eq:pbe4}.
This is valid as long as $\epsilon_1$ is a constant, so we use Eq.~\eqref{eq:phi_reac} for both BEM-BEM and FEM-BEM coupling simulations with constant $\epsilon_1$.

@@

We start with the variational formulation of the internal problem. Applying integration by parts to the first equation of~\eqref{eq:pbe_vp} we have, for every $v \in H_0^1(\Omega_1)$,
% 
\begin{equation}
\label{eq:fem}
 \left\langle \epsilon_1 \nabla \phi_1, \nabla v \right\rangle_{\Omega_1}  -  \left\langle  \epsilon_1\partial_n \phi_1, v \right\rangle_\Gamma =  \left\langle \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k),  v\right\rangle_{\Omega_1},
\end{equation}
%
where $v$ is a test function, and $\left\langle\varphi,v\right\rangle_\Gamma = \int_\Gamma \varphi(\mathbf{x})v(\mathbf{x})\,\mathrm{d}\mathbf{x}$ and $\left\langle\varphi,v\right\rangle_{\Omega_1} = \int_{\Omega_1} \varphi(\mathbf{x})v(\mathbf{x})\,\mathrm{d}\mathbf{x}$ are the inner products on the surface and in the domain, respectively.
For the external problem with BEM, we define the Dirichlet trace~\cite{MR2361676} 
\begin{align*}
% \label{eq:trace_map}
\gamma:  H^1(\Omega_2) &\rightarrow H^{\frac{1}{2}}(\Gamma), & \gamma f(x) & := \lim_{\Omega_2 \ni \mathbf{y} \rightarrow \mathbf{x} \in \Gamma}  f(\mathbf{y}),
\end{align*}
and we use the direct formulation from the second equation of Eq.~\eqref{eq:pbe} to obtain
\begin{align*}
\tfrac{\phi_1}{2} - K_{Y}^{\Gamma}\gamma \phi_1 + \tfrac{\epsilon_1}{\epsilon_2}V_{Y}^{\Gamma}  \lambda_1 & = 0.
\end{align*}
$V$ and $K$ are the single-layer and double-layer operators as defined in Equation~\eqref{eq:all_op}.
%as
%
%\begin{align}\label{eq:single_double}
%V_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma g_i(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
%K_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma \frac{\partial g_i}{\partial\mathbf{n}'}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
%K^{\prime\Gamma}_i\varphi (\mathbf{x}) &= \oint_\Gamma \frac{g_i}{\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
%W^\Gamma_i\varphi (\mathbf{x}) &= - \oint_\Gamma \frac{\partial^2 g_i}{\partial\mathbf{n}'\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'
%\end{align}
%
%where $i \in \{L,Y\}$, $\varphi(\mathbf{x})$ can be any distribution over $\Gamma$, and
%
%\begin{align}\label{eq:green_func}
%g_L(\mathbf{x},\mathbf{x}')=\frac{1}{4\pi|\mathbf{x}-\mathbf{x}'|} \nonumber \\
%g_Y(\mathbf{x},\mathbf{x}')=\frac{e^{-\kappa|\mathbf{x}-\mathbf{x}'|}}{4\pi|\mathbf{x}-\mathbf{x}'|}
%\end{align}
%
%are the corresponding free-space Green's functions.

Then, the coupling problem can be written as: \textit{Find $ \phi_1 \in H^1(\Omega_1)$ and $\lambda_2 \in H^{-\frac{1}{2}}(\Gamma)$ such that for all $v \in H^1(\Omega_1)$ and $\zeta \in H^{-\frac{1}{2}}(\Gamma)$},
\begin{subequations}
\label{eq:standard_fem_bem}
\begin{align} 
 \left\langle  \epsilon_1 \nabla \phi_1, \nabla v \right\rangle_{\Omega_1}  - \left\langle \epsilon_1 \lambda_2, v \right\rangle_\Gamma &=   \left\langle  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k),  v \right\rangle_{\Omega_1}, \\[3mm] 
  \left\langle \left\langle\tfrac{1}{2} I - K_{Y}^{\Gamma}\right) \gamma \phi_1, \zeta \right\rangle_\Gamma + \tfrac{1}{\epsilon_2} \left\langle V_{Y}^{\Gamma}\epsilon_1\lambda_2, \zeta \right\rangle_\Gamma &=0.
\end{align}
\end{subequations}
Note that in the case where $\epsilon_1$ is constant, then each $\epsilon_1$ can be moved outside of the inner product it is inside.

@@

When discretised, this can also be written in matrix form. Let $\vec{\phi}_1 := [\phi_1^1, \dots, \phi_1^j]^T$ be the vector of canonical basis
functions of the finite element space $V_{h}^{j}\subset H^1(\Omega_1)$, %$\vec{\phi}_2 := [\phi_2^1, \dots, \phi_2^k]^T$ - the vector of canonical basis functions of $W_{h}^{k}$,  
and let $\vec{\lambda}_2 := [\lambda_2^1, \dots, \lambda_2^l]^T$ be the vector of canonical basis
functions of $\Lambda_{h}^{l}\subset H^{-\frac{1}{2}}(\Gamma)$. % and $\vec{\widetilde{\phi}} := [\widetilde{\phi}^1, \dots, \widetilde{\phi}^m]^T$ be the vector of canonical basis functions of  $M_{h}^{m}$
% $T:\Omega_1 \rightarrow \Gamma$ and $E:\Gamma \rightarrow \Omega_1$ trace and extendable operators respectively.
We define the following matrices associated with the corresponding bilinear forms
\begin{align*}
A_{\alpha \beta} &= \left\langle\epsilon_1\nabla\phi_1^{\alpha}, \nabla \phi_1^{\beta} \right\rangle_{\Omega_1},&
M_{\alpha \beta} &= \left\langle \epsilon_1\lambda^{\beta}_2,\phi_1^{\alpha}\right\rangle_{\Gamma},\\
K_{\alpha \beta} &= \left\langle K_{Y}^{\Gamma} \gamma \phi^{\alpha}_1, \lambda^{\beta}_2 \right\rangle_{\Gamma},&
V_{\alpha \beta} &= \left\langle V_{Y}^{\Gamma} \epsilon_1\lambda^{\alpha}_2, \lambda^{\beta}_2 \right\rangle_{\Gamma},\\
I_{\alpha \beta} &= \left\langle \gamma \phi^{\alpha}_1, \lambda^{\beta}_2 \right\rangle_{\Gamma},
\end{align*}
\mscomment{As $I$ is not equal to the identity matrix, we should maybe change the letter we use? I'd usually change it to $M$ but we've also already used that}
and vector associated with the corresponding linear form
\begin{equation*}
\vec{f}_{\beta} := \left\langle  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k),  \phi_1^{\beta} \right\rangle_{\Omega_1}.
\end{equation*}
Using the above definitions, the discrete problem in \eqref{eq:standard_fem_bem} can be written in the following blocked matrix form:
\begin{align}\label{eq:fembem_matrix}
\begin{bmatrix}
A & -M^T \\  
\left(\tfrac12 I - K \right) \gamma &  \tfrac{1}{\epsilon_2} V 
\end{bmatrix}
\begin{bmatrix}
\vec{\phi}_1 \\  
\vec{\lambda}_2
\end{bmatrix}
= 
\begin{bmatrix}
\vec{f} \\  
0
\end{bmatrix}.
\end{align}

>>>>

Several possible boundary integral formulations of \eqref{eq:pbe} exist.~\cite{search2022towards} The simplest form was presented by Yoon and Lenhoff in 1991\cite{YoonLenhoff1990} and is known as the \emph{direct formulation}. However, the resulting system is usually ill-conditioned. Here, we use the better-conditioned formulation presented by Lu and co-workers,~\cite{LuETal2006,LuETal2009,debuhr2016dashmm} which reads
%
\begin{align}\label{eq:lu}
    \tfrac{\phi_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) - \left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)\phi_2 + \left(V_Y^\Gamma - V_L^\Gamma\right)\lambda_2 &= \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|},
     \nonumber \\
    \tfrac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)\phi_2 +  \tfrac{\lambda_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) + \left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\lambda_2 &= \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}\right),
\end{align}
where $\phi_2 = \phi_2(\mathbf{x}_\Gamma)$ is the potential on $\Gamma$ as we approach from $\Omega_2$ ({\it ie.} the exterior Dirichlet trace),
and $\lambda_2 = \frac{\partial}{\partial \mathbf{n}}\phi_2$ is the normal derivative $\Gamma$ as we approach from $\Omega_2$ ({\it ie.} the exterior Neumann trace).
Note that we can obtain $\phi_1$ and $\lambda_1$ from $\phi_2$ and $\lambda_2$ by applying the interface conditions \eqref{eq:pbe3} and \eqref{eq:pbe4}.
The operators $V$, $K$, $K^{\prime}$, and $W$ that appear in Equation \eqref{eq:lu} are the single-layer, double-layer, adjoint double-layer, and hypersingular operators for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels. These are defined %in Equation~\eqref{eq:single_double} and 
by
%
\begin{align}\label{eq:all_op}
V_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma g_i(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
K_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma \frac{\partial g_i}{\partial\mathbf{n}'}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
K^{\prime\Gamma}_i\varphi (\mathbf{x}) &= \oint_\Gamma \frac{g_i}{\partial\mathbf{n}}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
W^\Gamma_i\varphi (\mathbf{x}) &= - \oint_\Gamma \frac{\partial^2 g_i}{\partial\mathbf{n}'\partial\mathbf{n}}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',
\end{align}
%
where $i \in \{L,Y\}$, $\varphi(\mathbf{x})$ can be any distribution over $\Gamma$, and %Green's functions $g_L, g_Y$ were defined in Equation~\eqref{eq:green_func}.
\begin{align}\label{eq:green_func}
g_L(\mathbf{x},\mathbf{x}')=\frac{1}{4\pi|\mathbf{x}-\mathbf{x}'|} \nonumber \\
g_Y(\mathbf{x},\mathbf{x}')=\frac{e^{-\kappa|\mathbf{x}-\mathbf{x}'|}}{4\pi|\mathbf{x}-\mathbf{x}'|}
\end{align}
are the corresponding free-space Green's functions.

@@

Having computed the electrostatic potential with Eq.~\eqref{eq:lu}, we obtain the reaction potential ($\phi_r$) in Eq.~\eqref{eq:dG} by subtracting the Coulombic component from $\phi_1$. This gives\cite{CooperBardhanBarba2014}
%
\begin{align} \label{eq:phi_reac}
\phi_{r}(\mathbf{r}) = - K_{L}^{\Gamma} \phi_1(\mathbf{r}) + V_{L}^{\Gamma}  \lambda_1(\mathbf{r}),
\end{align}
%
where $\mathbf{r}\in\Omega_1$.
This is valid as long as $\epsilon_1$ is a constant, so we use Eq.~\eqref{eq:phi_reac} for both BEM-BEM and FEM-BEM coupling simulations with constant $\epsilon_1$.

@@

We start with the variational formulation of the internal problem. Applying integration by parts to the first equation of~\eqref{eq:pbe_vp} we have, for every $v \in H_0^1(\Omega_1)$,
% 
\begin{equation}
\label{eq:fem}
 \left\langle \epsilon_1 \nabla \phi_1, \nabla v \right\rangle_{\Omega_1}  -  \left\langle  \epsilon_1\partial_n \phi_1, v \right\rangle_\Gamma =  \left\langle \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k),  v\right\rangle_{\Omega_1},
\end{equation}
%
where $v$ is a test function, and $\left\langle\varphi,v\right\rangle_\Gamma = \int_\Gamma \varphi(\mathbf{x})v(\mathbf{x})\,\mathrm{d}\mathbf{x}$ and $\left\langle\varphi,v\right\rangle_{\Omega_1} = \int_{\Omega_1} \varphi(\mathbf{x})v(\mathbf{x})\,\mathrm{d}\mathbf{x}$ are the inner products on the surface and in the domain, respectively. To ensure clarity, we use a shorthand notation for the right-hand side where $\left\langle \cdot, \cdot \right\rangle_{\Omega_1}$ denotes duality paring.
For the external problem with BEM, we define the Dirichlet trace~\cite{MR2361676} 
\begin{align*}
% \label{eq:trace_map}
\gamma:  H^1(\Omega_2) &\rightarrow H^{\frac{1}{2}}(\Gamma), & \gamma f(x) & := \lim_{\Omega_2 \ni \mathbf{y} \rightarrow \mathbf{x} \in \Gamma}  f(\mathbf{y}),
\end{align*}
and we use the direct formulation from the second equation of Eq.~\eqref{eq:pbe} to obtain
\begin{align*}
\tfrac{\phi_1}{2} - K_{Y}^{\Gamma}\gamma \phi_1 + \tfrac{\epsilon_1}{\epsilon_2}V_{Y}^{\Gamma}  \lambda_1 & = 0.
\end{align*}
$V$ and $K$ are the single-layer and double-layer operators as defined in Equation~\eqref{eq:all_op}.
%as
%
%\begin{align}\label{eq:single_double}
%V_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma g_i(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
%K_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma \frac{\partial g_i}{\partial\mathbf{n}'}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
%K^{\prime\Gamma}_i\varphi (\mathbf{x}) &= \oint_\Gamma \frac{g_i}{\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
%W^\Gamma_i\varphi (\mathbf{x}) &= - \oint_\Gamma \frac{\partial^2 g_i}{\partial\mathbf{n}'\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'
%\end{align}
%
%where $i \in \{L,Y\}$, $\varphi(\mathbf{x})$ can be any distribution over $\Gamma$, and
%
%\begin{align}\label{eq:green_func}
%g_L(\mathbf{x},\mathbf{x}')=\frac{1}{4\pi|\mathbf{x}-\mathbf{x}'|} \nonumber \\
%g_Y(\mathbf{x},\mathbf{x}')=\frac{e^{-\kappa|\mathbf{x}-\mathbf{x}'|}}{4\pi|\mathbf{x}-\mathbf{x}'|}
%\end{align}
%
%are the corresponding free-space Green's functions.

Then, the coupling problem can be written as: \textit{Find $ \phi_1 \in H^1(\Omega_1)$ and $\lambda_1 \in H^{-\frac{1}{2}}(\Gamma)$ such that for all $v \in H^1(\Omega_1)$ and $\zeta \in H^{-\frac{1}{2}}(\Gamma)$},
\begin{subequations}
\label{eq:standard_fem_bem}
\begin{align} 
 \left\langle  \epsilon_1 \nabla \phi_1, \nabla v \right\rangle_{\Omega_1}  - \left\langle \epsilon_1 \lambda_1, v \right\rangle_\Gamma &=   \left\langle  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k),  v \right\rangle_{\Omega_1}, \\[3mm] 
  \left\langle \left\langle\tfrac{1}{2} I - K_{Y}^{\Gamma}\right) \gamma \phi_1, \zeta \right\rangle_\Gamma + \tfrac{1}{\epsilon_2} \left\langle V_{Y}^{\Gamma}\epsilon_1\lambda_1, \zeta \right\rangle_\Gamma &=0.
\end{align}
\end{subequations}
Note that in the case where $\epsilon_1$ is constant, then each $\epsilon_1$ can be moved outside of the inner product it is inside.

@@

When discretised, this can also be written in matrix form. Let $\vec{\phi}_1 := [\phi_1^1, \dots, \phi_1^j]^T$ be the vector of canonical basis
functions of the finite element space $V_{h}^{j}\subset H^1(\Omega_1)$, %$\vec{\phi}_2 := [\phi_2^1, \dots, \phi_2^k]^T$ - the vector of canonical basis functions of $W_{h}^{k}$,  
and let $\vec{\lambda}_1 := [\lambda_1^1, \dots, \lambda_1^l]^T$ be the vector of canonical basis
functions of $\Lambda_{h}^{l}\subset H^{-\frac{1}{2}}(\Gamma)$. % and $\vec{\widetilde{\phi}} := [\widetilde{\phi}^1, \dots, \widetilde{\phi}^m]^T$ be the vector of canonical basis functions of  $M_{h}^{m}$
% $T:\Omega_1 \rightarrow \Gamma$ and $E:\Gamma \rightarrow \Omega_1$ trace and extendable operators respectively.
We define the following matrices associated with the corresponding bilinear forms
\begin{align*}
A_{\alpha \beta} &= \left\langle\epsilon_1\nabla\phi_1^{\alpha}, \nabla \phi_1^{\beta} \right\rangle_{\Omega_1},&
\tilde{M}_{\alpha \beta} &= \left\langle \epsilon_1\lambda^{\beta}_1, \gamma \phi_1^{\alpha}\right\rangle_{\Gamma},\\
K_{\alpha \beta} &= \left\langle K_{Y}^{\Gamma} \gamma \phi^{\alpha}_1, \lambda^{\beta}_1 \right\rangle_{\Gamma},&
V_{\alpha \beta} &= \left\langle V_{Y}^{\Gamma} \epsilon_1\lambda^{\alpha}_1, \lambda^{\beta}_1 \right\rangle_{\Gamma},\\
M_{\alpha \beta} &= \left\langle \gamma \phi^{\alpha}_1, \lambda^{\beta}_1 \right\rangle_{\Gamma},
\end{align*}
and vector associated with the corresponding linear form
\begin{equation*}
\vec{f}_{\beta} := \left\langle  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k),  \phi_1^{\beta} \right\rangle_{\Omega_1}.
\end{equation*}
Using the above definitions, the discrete problem in \eqref{eq:standard_fem_bem} can be written in the following blocked matrix form:
\begin{align}\label{eq:fembem_matrix}
\begin{bmatrix}
A & -\tilde{M}^T \\  
\left(\tfrac12 M - K \right) &  \tfrac{1}{\epsilon_2} V 
\end{bmatrix}
\begin{bmatrix}
\vec{\phi}_1 \\  
\vec{\lambda}_1
\end{bmatrix}
= 
\begin{bmatrix}
\vec{f} \\  
0
\end{bmatrix}.
\end{align}
